Generalized Tractability

### 2023-06-07 GeneralizedTractability_230529.tex
Updates from Overleaf

Define
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \qquad \text{by \eqref{eq:comprestr}} \\
	\nonumber
	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', \ 1 \le N \le M(d) \\
 \nonumber
 & \hspace{20ex}\text{by \eqref{eq:implicate_a_rest}.} 
 \intertext{
 This last statement holds for all $N \le M(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
 \comp(\varepsilon,d)
	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d',\ 1 \le N \le M(d). \label{eq:compUP}
\end{align}

@@

For $(\varepsilon^{-1}, d) \in \Omega$, define
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 . 
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > E(d), \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

\end{enumerate}
Thus, in all cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.

\begin{theorem}\label{thm_main_rest_tract}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable on $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
\begin{equation} \label{eq:rest_tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal  tractability parameters is
\[
\cp_{\textup{opt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

\begin{proof}
    \textbf{Sufficient Condition:}\\
We adapt the argument in the proof of the sufficient condition for Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.  Suppose that \eqref{eq:rest_tractiff4} holds for some $\vp \ge 0$. Fix any $(\varepsilon^{-1},d) \in \Omega$.

Define the interval
\begin{equation} \label{eq:hIdef}
\hI_{d}:=\begin{cases} 
\{1,\ldots, M(d)\}, & M(d) < \infty, \\
\naturals, & M(d) = \infty.
\end{cases}
\end{equation}
Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{\cdot,d}^{-1},d,\vp)$ is non-decreasing. For any $N\in \hI_d$ and any $n \in \hI_d \setminus \{1, \ldots, N-1\}$,
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d \in \naturals, \ N \in \hI_d, \ n \in \hI_d \setminus \{1, \ldots, N-1\}.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via \eqref{eq:comp_def} for all $(\varepsilon^{-1},d) \in \Omega$:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \\
	\nonumber
	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\}\\
	\nonumber
	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \biggr\} \;  \forall N \in \naturals, \quad \text{by \eqref{eq:implicate_a_rest}} \\ 
	& \le  T(\varepsilon^{-1},d,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d,\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \Biggr] \quad \forall N \in \naturals. \label{eq:compUP_rest}
\end{align}

it follows from \eqref{eq:compUP_rest} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:rest_tractiff4}}}
       \Biggr ] 
        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
       & \le T(\varepsilon^{-1},d,\vp) 
       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}  
\end{align*}
It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:rest_tractiff4}.

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall (\varepsilon^{-1}, d) \in \Omega.
\end{equation}

For $(\varepsilon^{-1}, d) \in \Omega$, define the integers 
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]
It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that since $T(\cdot,d,\vp)$ is non-decreasing, we have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall (\varepsilon^{-1},d)\in\Omega.
\]
For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values 
\[
I_{d}:=\begin{cases} 
\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
\]

>>>>

Define
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =\lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1.
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

\subsection{Strong Tractability on a Restricted Domain}

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \qquad \text{by \eqref{eq:comprestr}} \\
	\nonumber
	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', \ 1 \le N \le M(d) \\
 \nonumber
 & \hspace{20ex}\text{by \eqref{eq:implicate_a_rest}.} 
 \intertext{
 This last statement holds for all $N \le M(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
 \comp(\varepsilon,d)
	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d',\ 1 \le N \le M(d). \label{eq:compUP_rest}
\end{align}

@@

For $(\varepsilon^{-1}, d) \in \Omega$, define the positve integers
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1 . 
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > E(d), \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
\[
I_{d,\vp}:=\begin{cases} 
\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather}
\nonumber
 K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
  \label{eq:rest_strong_ineq}
 \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
\end{gather}

\end{enumerate}
Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.

\subsection{Tractability on a Restricted Domain}

\begin{theorem}\label{thm_main_rest_tract}
Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.  A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
\begin{equation} \label{eq:rest_tractiff}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
\[
\cp_{\textup{ropt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{rtrct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{rtrct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

\begin{proof}
    \textbf{Sufficient Condition:}\\
Fix $d$.  If $M(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [E(d), \infty)$.

For the case $M(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $d'=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)$:
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{M(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
        \Biggr] \\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{M(d), d}^{-1},d,\vp)} \right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & \le T(\varepsilon^{-1},d,\vp) \underbrace{\left[L_{\vp} + \frac{2}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & =  C_{\vp}T(\varepsilon^{-1},d,\vp).
\end{align*}
This means that we have strong $T$-tractability on the restricted domain $\Omega$ via \eqref{eq:rest_tract_def}, and verifies the sufficiency of \eqref{eq:rest_tractiff}.

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability on the restricted domain. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall \varepsilon > E(d),\ d \in \naturals.
\end{equation}

For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers 
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]
It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that since $T(\cdot,d,\vp)$ is non-decreasing, we have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > E(d),\ d \in \naturals.
\]
For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
\[
I_{d,\vp}:=\begin{cases} 
\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
\]

%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\end{enumerate}
Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
\bigskip
